Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Plurality of continuations.
Tightend more prose on store-allocated resutls

To achieve this linearity for continuation, we allocate an address for the value position
when we create the continuation.  This address and the tail address
are both determined by the label of the application point, so the
space becomes linear and the overall complexity drops to cubic. 
This is a critical abstraction in languages with $n$-ary functions,
since otherwise the continuation space grows super-exponentially.
% In theory, this aggressive distinction between continuations might buy
% additional precision, but in practice, it does not.

The important rules that change are the following, specialized to 0-CFA:

@@

This extra store-allocation is effectively naming all intermediate
results, and thus the precision aligns with an analysis specialized to
ANF. We can also play a representation trick in 0-CFA and remove
$\menv$. In monovariant analyses, variables map to themselves, meaning
$\menv$ is effectively the identity function. That degeneration, in
turn, allows us to discard it from the analysis.

>>>>

To achieve this linearity for continuations, we allocate an address
for the value position when we create the continuation.  This address
and the tail address are both determined by the label of the
application point, so the space becomes linear and the overall
complexity drops to cubic.  This is a critical abstraction in
languages with $n$-ary functions, since otherwise the continuation
space grows super-exponentially.
% In theory, this aggressive distinction between continuations might buy
% additional precision, but in practice, it does not.

If we specialize to 0CFA, the evaluation rules become:

@@

% This extra store-allocation is effectively naming all intermediate
% results, and thus the precision aligns with an analysis specialized to
% ANF. We can also play a representation trick in 0-CFA and remove
% $\menv$. In monovariant analyses, variables map to themselves, meaning
% $\menv$ is effectively the identity function. That degeneration, in
% turn, allows us to discard it from the analysis.
